Visualizing probability distributions across bivariate cyclic temporal granularities

### 2020-04-23 main.Rmd
\todo[inline]{Can you use the same units shown in Fig 1?}
{Expand  into  a paragraph - how does  it illustrate the linear granularities? How does  hour, day,... relate to G...}

\noindent This implies that the granules in a linear granularity are non-overlapping, continuous and ordering is maintained. The indexing for each granule can also be associated with textual representation, called the label.<!--The label can be mapped to index for input and the index can later be mapped to this label for output. When the label set is exactly the integers, the granularities are called "full-integer" labeled granularity, such as in Definition \ref{def:linear}. Some calendar operations will only work on full-integer labeled granularities, while others can be implemented using more flexible labelings.-->

\autoref{fig:linear-time} illustrates the linear time granularities. \todo[inline]{Expand  into  a paragraph - how does  it illustrate the linear granularities? How does  hour, day,... relate to G...} <!--, each of which are non-repeating in nature and arranged from past to future. If we consider $T$ hours, we will have $\lfloor T/24\rfloor$ days, $\lfloor T/(24*7)\rfloor$ weeks and so on.-->

```{r linear-time, echo=FALSE, out.width = "100%", fig.cap="The time domain distributed as linear granularities hours, days, weeks and months. These are ordered with ordering guided by integers and hence is unidirectional and non-repeating."}
knitr::include_graphics("Figs/linear-arr2.png")
```

@@

\begin{example} 
{\rm minute = G$_{60}(\text{second})$, hour = G$_{60}(\text{minute})$, day = G$_{24}(\text{hour})$.}\todo[inline]{Can you use the same units shown in Fig 1?}
\end{example}

>>>>

\noindent This implies that the granules in a linear granularity are non-overlapping, continuous and ordering is maintained. The indexing for each granule can also be associated with textual representation, called the label.<!--The label can be mapped to index for input and the index can later be mapped to this label for output. When the label set is exactly the integers, the granularities are called "full-integer" labeled granularity, such as in Definition \ref{def:linear}. Some calendar operations will only work on full-integer labeled granularities, while others can be implemented using more flexible labelings.--> A discrete time model often uses a fixed smallest linear granularity named by @Bettini1998-ed **bottom granularity**.

\autoref{fig:linear-time} illustrates the linear time granularities. Here, "hour" is a linear granularity which is a mapping from index set to hourly time domain. Similarly, "day", "week", "month" and "year" are also linear granularities which maps from index set to subsets of the hourly time domain. For example, day($0$) =  {hour($0$), hour($1$), hour($2$), \dots, hour($23$)}, day($1$) =  {hour($24$), hour($25$), hour($26$), \dots, hour($47$)} and so on. Thus, if we have "hour" running from $\{0, 1, \dots,t\}$, we will have "day" running from $\{0, 1, \dots, \lfloor t/24\rfloor\}$. These linear granularities are ordered with ordering guided by the index set which is a set of integers. Hence, they are uni-directional and non-repeating.

\todo[inline]{Expand  into  a paragraph - how does  it illustrate the linear granularities? How does  hour, day,... relate to G...} <!--, each of which are non-repeating in nature and arranged from past to future. If we consider $T$ hours, we will have $\lfloor T/24\rfloor$ days, $\lfloor T/(24*7)\rfloor$ weeks and so on.-->

```{r linear-time, echo=FALSE, out.width = "100%", fig.cap="The time domain distributed as linear granularities hour, day, week, month and year. These are ordered with ordering guided by integers and hence is unidirectional and non-repeating."}
knitr::include_graphics("Figs/linear-arr3.png")
```

@@

\begin{example} 
{\rm day = G$_{24}(\text{hour})$, week = G$_{7}(\text{day})$.}
\end{example}
